Really Hard Instances for the Subgraph Isomorphism Problem

### 2015-09-22 paper/paper.tex
More
A phase transition

@@

\begin{figure*}[tb]
    \hskip-1.2cm\input{gen-graph-induced.tex}
    \setlength{\abovecaptionskip}{-2em}
    \caption{Behaviour of algorithms on the induced variant, shown in the style
    of \cref{figure:non-induced}.}\label{figure:induced}
\end{figure*}

@@

\begin{figure*}[tb]
    \hskip-1.2cm\input{gen-graph-sat.tex}
    \setlength{\abovecaptionskip}{-2em}
    \caption{Behaviour of other solvers on the induced variant on smaller graphs, shown in the style of
        \cref{figure:non-induced}. The second row shows the number of search nodes used by the Glasgow
        algorithm, the third row shows the number of decisions made by the Glucose SAT solver, and
    the fourth row shows the number of search nodes used by a clique encoding.}\label{figure:alt}
\end{figure*}

>>>>

\begin{figure}[tb]
    \input{gen-graph-phase-transition.tex}
    \caption{With a fixed a pattern size of 20, a target size of 150, a target density of 0.4, and
    varying pattern density, we observe a phase transition and complexity peak in the non-induced
    variant. Each point represents one instance.}
    \label{figure:phase-transition}
\end{figure}

Arbitrarily decide upon a pattern size of 20, a target size of 150, and a fixed target density of
0.40. \cref{figure:phase-transition}.

@@

\begin{figure*}[tb]
    \hskip-1.2cm\input{gen-graph-induced.tex}
    \setlength{\abovecaptionskip}{-3em}
    \caption{Behaviour of algorithms on the induced variant, shown in the style
    of \cref{figure:non-induced}.}\label{figure:induced}
\end{figure*}

@@

\begin{figure*}[tb]
    \hskip-1.2cm\input{gen-graph-sat.tex}
    \setlength{\abovecaptionskip}{-3em}
    \caption{Behaviour of other solvers on the induced variant on smaller graphs, shown in the style of
        \cref{figure:non-induced}. The second row shows the number of search nodes used by the Glasgow
        algorithm, the third row shows the number of decisions made by the Glucose SAT solver, and
    the fourth row shows the number of search nodes used by a clique encoding.}\label{figure:alt}
\end{figure*}
